### 2022-12-02 writing/manuscript.Rmd
removed old bootstrap code (no longer used)

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# I ran this code with n=10000 iterations and stored the results in results/bootstrap_res.csv. To save time when knitting, the chunk of code that produced this file will be skipped, and values will be read in from the saved document. However, the relevant code that produced the values in bootstrap_res.csv can be found below, for reproducibility.

# USED FOR DANCING
# loop n times and store all correlation coefficients in vector
danc_cors <- c()
for (i in 1:n) {
  danc_cors[i] <- boot(fulldata, "danc")
}

danc_cors <- data.frame(danc_cors)

# USED FOR SOOTHING A BABY
# loop n times and store all correlation coefficients in vector
baby_cors <- c()
for (i in 1:n) {
  baby_cors[i] <- boot(fulldata, "baby")
}

baby_cors <- data.frame(baby_cors)

# USED FOR HEALING THE SICK
# loop n times and store all correlation coefficients in vector
heal_cors <- c()
for (i in 1:n) {
  heal_cors[i] <- boot(fulldata, "heal")
}

heal_cors <- data.frame(heal_cors)

# USED FOR EXPRESSING LOVE
# loop n times and store all correlation coefficients in vector
love_cors <- c()
for (i in 1:n) {
  love_cors[i] <- boot(fulldata, "love")
}

love_cors <- data.frame(love_cors)

@@

# Plotting function
boot_plot <- function(x_var, color_var, title_var, annotation_var) {
  p <- ggplot(boot, aes(x = {{x_var}})) + 
    geom_histogram(aes(y = stat(density)), 
                   alpha = 0.4,
                   colour = color_var,
                   fill = color_var,
                   bins = 100) + 
    geom_density() +
    geom_vline(xintercept = 0, # aes(xintercept = mean({{x_var}})) 
               linetype = "dashed", size = 0.6, alpha = .5) + 
    labs(title = title_var,
         x= "Correlation Coefficients", y = "Density") +
    lims(x = c(-0.2,1), y = c(0, 15)) +
    theme_classic() +
    theme(text = element_text(size=9,  family = "serif"),
          axis.text.x = element_text(size = 8),
          plot.title = element_markdown(size = 9))

>>>>

@@

# Plotting function
boot_plot <- function(x_var, color_var, title_var, annotation_var) {
  p <- ggplot(boot, aes(x = {{x_var}})) + 
    geom_histogram(aes(y = stat(density)), 
                   alpha = 0.4,
                   colour = color_var,
                   fill = color_var,
                   bins = 100) + 
    geom_density() +
    geom_vline(xintercept = 0,
               linetype = "dashed", size = 0.6, alpha = .5) + 
    labs(title = title_var,
         x= "Correlation Coefficients", y = "Density") +
    lims(x = c(-0.2,1), y = c(0, 15)) +
    theme_classic() +
    theme(text = element_text(size=9,  family = "serif"),
          axis.text.x = element_text(size = 8),
          plot.title = element_markdown(size = 9))
